Stats

### 2022-08-10 stats/analysis.Rmd
add final figures

splithalf_plot
saveRDS(splithalf_plot, file = "../saves/gafo-splithalf-plot.rds")
# ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)
```

>>>>

splithalf_plot
saveRDS(splithalf_plot, file = "../saves/gafo-splithalf-plot.rds")

# ggsave("../figures/gafo_splithalf.png", width = 8, height = 2.5, scale = 1.2)
```
